% A workaround to allow relative paths in included subfiles
% that are to be compiled separately
% See https://tex.stackexchange.com/questions/153312/subfiles-inside-a-subfile-using-relative-paths
\providecommand{\main}{..}
\documentclass[\main/thesis.tex]{subfiles}

\begin{document}

% environment for abstract.
\begin{abstract}
Many datasets can be represented as networks or graphs, where sets of nodes are joined together in pairs by links or edges. In the past, many works have been done about complex network analysis in certain graphs, graphs where the network structure is exactly and deterministically known. Recently, in many cases, uncertainty or imprecise information becomes a critical impediment to understanding and effectively utilizing the information contained in the such graphs. There are many kinds of uncertainty in networks, such as edge uncertainty, node uncertainty, direction uncertainty and weight uncertainty. The problem of complex network analysis with uncertainty has become increasing important. However, only few studies take uncertainty into consideration.

In this thesis, we mainly focus on networks with edge uncertainty, networks where the existence of edges are uncertain. We propose efficient algorithms to solve problems such as link prediction, local community detection and entity ranking for networks with edge uncertainty. Finally, we conduct supervised, unsupervised and illustrative experiments to evaluate our algorithms, and all these experiments show that our algorithms work effectively.
\end{abstract}

\end{document}